---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# frostr2

<!-- badges: start -->
[![R-CMD-check](https://github.com/Riksrevisjonen/frostr2/workflows/R-CMD-check/badge.svg)](https://github.com/Riksrevisjonen/frostr2/actions)
[![Lifecycle:experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

frostr2 is an unofficial R client to MET Norway's Frost API. 

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("Riksrevisjonen/frostr2")
```

## Usage

### Initial setup 

In order to use the Frost API you will need to register an account with [MET Norway](https://frost.met.no/index.html). This will grant you a client id and secret that you should store in a safe place. 

To work with frostr2 it is recommended that you store the credentials as a set of environmental variables (MET_FROST_ID and MET_FROST_SECRET) available to R. You could either do this yourself or you could use the helper function `set_frost_client()`. Must users will typically benefit from setting environmental variables
at the user level.

```{r frost_client, eval=FALSE}
frostr2::set_frost_client(scope = "user") 
```

### Basic example 

```{r example, message=FALSE, warning=FALSE}
library(frostr2)

# Fetch observation data
df <- get_observations(
  sources = c("SN18700", "SN90450"),
  reference_time = "2010-04-01/2010-04-03",
  elements = c(
    "mean(air_temperature P1D)",
    "sum(precipitation_amount P1D)",
    "mean(wind_speed P1D)"
  )
)
head(df)
```

## For developers 

For development purposes it is recommended to turn off the session based caching. This can be done by setting the `FROSTR2_DISABLE_CACHING` environmental variable to `"TRUE"`. 

## Acknowledgments 

frostr2 is inspired by [frostr](https://github.com/imangR/frostr) which has developed by [Iman Ghayoornia](https://github.com/imangR). 
